\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-16 NAR_DRAFT.tex
new figure 1 and caption

\begin{figure}
  \begin{center}
  \includegraphics{figures/signatures_only.pdf}

  \rngcomment{Need more basic labels for each panel. E.g. ``Real breast tumor'', ``Real accumulated myeloid leukemia'', ``Simulated concentrated profile''}
  \end{center}
  \caption{Tumor mutation profiles.
  \rngcomment{Add explanation of how to read a profile. ``In each panel, the histograms show...''}
  \textbf{(a)} The observed mutation profile of a breast tumor \cite{Shi2018}.
  \textbf{(b)} The observed mutation profile of an acute myeloid leukemia \cite{Griffith2015}.
  \textbf{(c)} \rngcomment{Add a third (and possibly fourth) real tumor, with a more concentrated profile. So we can illustrate that our simulations aren't out of line with reality. Ideally two tumors of same type that have noticeably different profiles.}
  \textbf{(c)} A mutation profile used for simulating tumors, made up of equal proportions of COSMIC mutation signatures 1, 7, \& 11.
  \textbf{(d)} Equal proportions of signatures 1, 4, \& 5.
  \textbf{(e)} Equal proportions of signatures 1, 3, \& 5.
  }
  \label{NAR-sigfig}
 \end{figure}

>>>>

\begin{figure}
  \begin{center}
  \includegraphics{figures/signatures_only.pdf}
  \end{center}
  \caption{Tumor mutation profiles.
  In each panel, the y-axis is the proportion of total mutations in the tumor with each of the 96 substitution types shown on the x-axis.
  \textbf{(A)} The observed mutation profile of an acute myeloid leukemia used in our real data analysis \cite{Griffith2015}.
  \textbf{(B)} The observed mutation profile of a breast tumor we used in our real data analysis \cite{Shi2018}.
  \textbf{(C)} A mutation profile used for simulating tumors, made up of equal proportions of COSMIC mutation signatures 1, 7, \& 11.
  \textbf{(D)} Equal proportions of signatures 1, 4, \& 5.
  \textbf{(E)} Equal proportions of signatures 1, 3, \& 5.
  \textbf{(F)} The observed mutaiton profile of a real breast tumor obtained from supplementary materials in Alexandrov et al. (2019) \citep{Alexandrov2019}.
  \textbf{(G)} The observed mutaiton profile of a real breast tumor obtained from supplementary materials in Alexandrov et al. (2019) \citep{Alexandrov2019}.
  }
  \label{NAR-sigfig}
 \end{figure}
